Patterns of floral and chromosome evolution in Onagraceae: a fossil-calibrated supermatrix analysis

### 2014-05-08 manuscript.tex
fixed figure

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \toprule
         DNA Region & \# of Taxa & Aligned Length & Missing data (\%) & Taxon Coverage Density \\ 
	 \midrule
         ITS & 453 & 1746 & 13.2 & 0.87 \\
         trnL & 234 & 1429 & 55.2 & 0.45 \\
         rpl16 & 91 & 1414 & 82.6 & 0.17 \\
         rbcL & 77 & 1474 & 85.2 & 0.15 \\
         rps16 & 74 & 1016 & 85.8 & 0.14 \\
         rbcL & 64 & 1310 & 87.7 & 0.12 \\
         PgiC2 & 47 & 4028 & 91.0 & 0.09 \\
         matK & 37 & 921 & 92.9 & 0.07 \\
         ndhF & 37 & 2063 & 92.9 & 0.07 \\
         pgiC & 26 & 14709 & 95.0 & 0.05 \\
         R5 & 18 & 3129 & 96.6 & 0.03 \\
         \bottomrule
      \end{tabular}
   \end{adjustbox}
   \caption{Clusters of homologous sequences used to assemble the supermatrix.}
   \label{clusters}
\end{table*}

>>>>

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \toprule
         DNA Region & \# of Taxa & Aligned Length & Missing data (\%) & Taxon Coverage Density \\ 
	 \midrule
         ITS & 453 & 1746 & 13.2 & 0.87 \\
         trnL & 234 & 1429 & 55.2 & 0.45 \\
         rpl16 & 91 & 1414 & 82.6 & 0.17 \\
         rbcL & 77 & 1474 & 85.2 & 0.15 \\
         rps16 & 74 & 1016 & 85.8 & 0.14 \\
         rbcL2 & 64 & 1310 & 87.7 & 0.12 \\
         PgiC2 & 47 & 4028 & 91.0 & 0.09 \\
         matK & 37 & 921 & 92.9 & 0.07 \\
         ndhF & 37 & 2063 & 92.9 & 0.07 \\
         pgiC & 26 & 14709 & 95.0 & 0.05 \\
         R5 & 18 & 3129 & 96.6 & 0.03 \\
         \bottomrule
      \end{tabular}
   \end{adjustbox}
   \caption{Clusters of homologous sequences used to assemble the supermatrix.}
   \label{clusters}
\end{table*}
